A Classical Density-Functional Theory for Describing Water Interfaces

### 2011-08-26 paper/project.tex
A few edits to single rod and project

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
\needsworklater{ We develop a classical density functional theory for
  water by combining the fundamental-measure theory functional--which
  describes hard sphere fluids--with attractive interactions based on the 
  Statistical Associating Fluid Theory (SAFT).  Using
  this approximation, we are able to describe various properties of
  water near liquid-vapor and liquid-solid interfaces including water confined 
  to a slit and hydrophobic rods immersed in water.  This functional will be
  the 
  foundation for a efficient method for future work
  predicting the interactions of chemicals in aqueous solution on an
  atomic level.}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
\needsworklater{ We develop a classical density functional theory for
  water by combining the fundamental-measure theory functional--which
  describes hard sphere fluids--with attractive interactions based on the 
  Statistical Associating Fluid Theory (SAFT).  Using
  this approximation, we are able to describe various properties of
  water near liquid-vapor and liquid-solid interfaces, including water confined 
  to a hard-walled slit and hydrophobic rods immersed in water.  This functional 
  will be the foundation for a efficient method for future work
  predicting the interactions of chemicals in aqueous solution on an
  atomic level.}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figs/rods-energy-vs-distance}
\end{center}
\caption{ Energy versus separation for two identical hydrophobic rods with diameters
of 1 nm. }
\label{fig:rods-energy-vs-distance}
\end{figure}
